Cor Compare

### 2022-09-30 graphs_newt_snakes/corcompare.Rmd
more cor calc

all_cor_exp$group_exp=paste0(all_cor_exp$group, "_", all_cor_exp$experiment)
all_cor_exp$exp_group=paste0(all_cor_exp$experiment, "_", all_cor_exp$group)

@@

@@

@@

>>>>

all_cor_exp$group_exp=paste0(all_cor_exp$group, "_", all_cor_exp$experiment)
all_cor_exp$exp_group=paste0(all_cor_exp$experiment, "_", all_cor_exp$group)
all_cor_exp$group_exp_rep=paste0(all_cor_exp$group, "_", all_cor_exp$experiment, "_",all_cor_exp$rep)

@@

print("One mean per GA")

@@

print("Anovas from mean of A and B")
res.aov2ab <- aov(name ~ exp, data = exclude_c[which(exclude_c$exp!='D'),])
summary(res.aov2ab)
print("Anovas from mean of A and C")
res.aov2ac <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='D'),])
summary(res.aov2ac)
print("Anovas from mean of A and D")
res.aov2ad <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='C'),])
summary(res.aov2ad)
print("Anovas from mean of C and D")
res.aov2cd <- aov(name ~ exp, data = exclude_b[which(exclude_b$exp!='A'),])
summary(res.aov2cd)

print("One mean per rep")

all_the_means_byrep = all_cor_exp %>%
  group_by(group_exp_rep) %>%
  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)

all_the_means_byrep$exp <- str_split_fixed(all_the_means_byrep$group_exp_rep, "_", 6)[,5]

exclude_b <- all_the_means_byrep[which(all_the_means_byrep$exp!='B'),]
exclude_c <- all_the_means_byrep[which(all_the_means_byrep$exp!='C'),]

@@

ggplot(all_cor_exp) + 
  #geom_point(size = 2) +
  #geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, group=rep))+
  geom_density(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)*3,fill=factor(experiment)), alpha=0.4, position="identity")+
  #geom_xsidehistogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(experiment)), alpha=0.4, position="identity") +
  geom_ysideboxplot(aes(x = experiment, y=mean_newt_pheno_By_mean_snake_pheno, fill=factor(experiment)), orientation = "x") +
  scale_ysidex_discrete(guide = guide_axis(angle = 45))

#all_cor_exp$num_newts_By_num_snakes
ggplot(all_cor_exp) + 
  #geom_point(size = 2) +
  geom_line(aes(generation, mean_newt_pheno_By_mean_snake_pheno, group=group_exp_rep, color=factor(experiment)), size = .1,alpha=0.4)+
  #geom_density(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)*3,fill=factor(experiment)), alpha=0.4, position="identity")+
    geom_xsideline(aes(generation, num_newts_By_num_snakes, group=group_exp_rep, color=factor(experiment)), size = .1,alpha=0.4)+
  geom_ysideboxplot(aes(x = experiment, y=mean_newt_pheno_By_mean_snake_pheno, fill=factor(experiment)), orientation = "x") +
  scale_ysidex_discrete(guide = guide_axis(angle = 45))

ggplot(all_cor_exp) + 
  #geom_point(size = 2) +
  geom_line(aes(generation, num_newts_By_num_snakes, group=group_exp_rep, color=factor(experiment)), size = .1,alpha=0.4)+
  #geom_density(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)*3,fill=factor(experiment)), alpha=0.4, position="identity")+
    geom_xsideline(aes(generation, num_newts_By_num_snakes, group=group_exp_rep, color=factor(experiment)), size = .1,alpha=0.4)+
  geom_ysideboxplot(aes(x = experiment, y=mean_newt_pheno_By_mean_snake_pheno, fill=factor(experiment)), orientation = "x") +
  scale_ysidex_discrete(guide = guide_axis(angle = 45)) 
```
